Implementing Capon Beamforming on a GPU for Real-Time Cardiac Ultrasound Imaging

### 2013-03-13 HRUIonGPU/jrnl_article.tex
adjusted plots

For high $L$ and $N_b$ values the two methods are equal. However, for lower values, BS Capon provides higher resolution than what is possible with small subarrays. We see that the resolution for BS Capon gradually decreases due to an automatically increase in diagonal loading (See end of Section \ref{sec:bs}). If this is compensated for, BS Capon will provide resolution almost equal to Capon (with $L=M/2$) for all values except $N_b=1$ \cite{Nilsen2009}. For $N_b=1$ the resolution is worse than for DAS because of a triangular apodization caused by subarray averaging. In element space, resolution decays rapidly as a result of a reduced effective adaptive aperture. For $N_b=3$, BS Capon still provides approximately 1 mm improved resolution over DAS. However, note that resolution for the Capon beamformer highly depends on image SNR and the choice of parameters. Thus, different SNR scenarios and choices of parameters will give different results. It is also worth noting that Capon beamforming in this example performs worse than DAS for small subarrays. For small values of $L$, there are not enough degrees of freedom in order perfectly steer a zero at each point target.

\begin{figure}
\centering
\includegraphics[width=3in]{gfx/speed_res_trade.png}
\caption{Trade-off between resolution and speed by reducing subarray size or reducing beamspace dimension (based on Fig. \ref{fig:phantom}). As $L$ or $N_b$ gets smaller, the execution time is reduced (Fig. \ref{fig:bench} and \ref{fig:benchBS}). When $N_b$ is varied, $L$ is fixed on 32.}
\label{fig:speed_res_trade}
\end{figure}

>>>>

For high values of $L$ and $N_b$ the two methods are equal, but for lower values, BS Capon provides improved resolution compared to using small subarrays. We see that the resolution for BS Capon gradually decreases due to an automatic increase in diagonal loading (See end of Section \ref{sec:bs}). If we compensated by reducing $d$, BS Capon will provide resolution almost equal to Capon (with $L=M/2$) for all values except $N_b=1$ \cite{Nilsen2009}. For $N_b=1$ the resolution is worse than for DAS because of a triangular apodization caused by subarray averaging. In element space, resolution decays rapidly as a result of a reduced effective adaptive aperture. For $N_b=3$, BS Capon still provides approximately 1 mm improved resolution over DAS. However, note that resolution of the Capon beamformer strongly depends on image SNR and the choice of parameters. Thus, different SNR scenarios and choices of parameters will lead to different results. It is also worth noting that Capon beamforming in this example performs worse than DAS for small subarrays. For small values of $L$, the amount of robustification is too high in order to perfectly steer a zero at each point target. The Capon beamformer therefore produce a result worse than DAS.

\begin{figure}
\centering
\includegraphics[width=3in]{gfx/speed_res_trade_d=0-01.png}
\caption{Trade-off between resolution and speed by reducing subarray size or reducing beamspace dimension (based on Fig. \ref{fig:phantom}). As $L$ or $N_b$ gets smaller, the execution time is reduced (Fig. \ref{fig:bench} and \ref{fig:benchBS}). When $N_b$ is varied, $L$ is fixed on 32.}
\label{fig:speed_res_trade}
\end{figure}
